Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}

### 2020-08-04 large_experiment_processing.Rmd

---
title: "Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}"
author: "Laurent Gatto, Sebastian Gibb and Johannes Rainer"
output:
    BiocStyle::pdf_document
---

@@

Note that there are also dedicated *filter* functions to subset an
`MSnExp` object such as `filterFile`, `filterMsLevel`, `filterRt`, `filterMz`,
`filterPrecursorMz` or `filterIsolationWindow`. In the example below we use the
`filterRt` function to further subset our data to contain only spectra acquired
within a certain time range.

@@

```{r precursor-selection-plot-1}
system.time(
    plot(ms_sub[[1]])
)["elapsed"]
```

@@

```{r precursor-selection-plot-normalized}
system.time(
    plot(ms_sub[[1]])
)["elapsed"]
```

>>>>

---
title: "Supplementary data for: \\textit{`MSnbase`, efficient and elegant R-based processing and visualisation of raw mass spectrometry data}"
author: "Laurent Gatto, Sebastian Gibb and Johannes Rainer"
output:
    BiocStyle::pdf_document:
        includes:
            in_header: "header.sty"
---

@@

Note that there are also dedicated *filter* functions to subset an
`MSnExp` object such as `filterFile`, `filterMsLevel`, `filterRt`, `filterMz`,
`filterPrecursorMz` or `filterIsolationWindow`. In the example below we use the
`filterRt` function to further subset our data to keep only spectra acquired
within a certain time range.

@@

```{r precursor-selection-plot-1, fig.cap = "Example spectrum of the data set."}
system.time(
    plot(ms_sub[[1]])
)["elapsed"]
```

@@

```{r precursor-selection-plot-normalized, fig.cap = "Example spectrum after cleaning."}
system.time(
    plot(ms_sub[[1]])
)["elapsed"]
```
